{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-12-09 main.tex
Increment

	\subsection{Different Bases of $\mathbb{L}^2$}

	\paragraph{b-spline Basis}

	\paragraph{Fourier Basis}

>>>>

	\subsection{Different Bases of $\mathbb{L}^2$}
	Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.
	\paragraph{b-spline Basis}

	\paragraph{Fourier Basis}
	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions.
	\begin{equation}
		S_{FB, i}(x) = \begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
